Estimating individual subjective values of emotion regulation strategies

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
knitted document
knitted doc

 Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
 SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=0.002$), but not with flexible ER. 

@@

wordcount         : "about 9000"

>>>>

 Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=.155$).
 SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=.002$), but not with flexible ER. 

@@

wordcount         : "9432"

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

\abstract{%
Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
Perceived costs of ER strategies in the form of effort, however, are highly subjective.
Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
However, SVs of ER strategies have not been determined so far.
We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process.
\(N=120\) participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
Afterwards, individual SVs were determined using the new CAD paradigm.
SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<0.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=0.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=0.155\)).
SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=0.002\)), but not with flexible ER.
With our paradigm, we were able to determine subjective values.
The trait character of the values will be discussed.
}

>>>>

\abstract{%
Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
Perceived costs of ER strategies in the form of effort, however, are highly subjective.
Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
However, SVs of ER strategies have not been determined so far.
We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process.
\(N=120\) participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
Afterwards, individual SVs were determined using the new CAD paradigm.
SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=.155\)).
SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=.002\)), but not with flexible ER.
With our paradigm, we were able to determine subjective values.
The trait character of the values will be discussed.
}
